---
title: "README"
author: "LGD"
date: "20/05/2023"
output:
  github_document:
    toc: true
    toc_depth: 3
---

enGlimpse is a package of tools for working with the output of biology and microscopy experiments in R. 
It includes functions for common visualisation and normalisation things that you need to do. 

The visualisation functions are **limpsing** or having a **squiz** at the output of plate based biology experiments. 
The normalisation function is for **eggresR**ing to remove linear trends.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation
```{r, echo = TRUE, results='hide', message = FALSE}

#install devtools if needed
if(!require("devtools")) install.packages("devtools")
#load devtools
library(devtools)

#install lifeTimes from github
install_github("somaSystems/enGlimpse")

```


## glancer and squiz demonstration data
```{r}
#demonstration data in the format of a 96 well plate

set.seed(1)
df_to_glimpse <- data.frame(
  Row = rep(c(1:8), times = 12), #Rows as numbers
  Column = rep(c(1:12), each = 8), #Columns as numbers 
  exp_value = runif(96,-10,10)) #Measured variables

```

## glancer
For having a glance at the data
```{r, warning=FALSE}

library(enGlimpse)
glancer(df_to_glimpse, variable_to_squiz ="exp_value" )

```

## squiz
For having a squiz at the data
```{r}
squiz(df_to_glimpse, picked_variable = "exp_value")
```

## eggresR demonstration data

```{r}
set.seed(42)  # Set seed for reproducibility

n <- 800  # Number of data points
x <- runif(n, 0, 2000)  # Generate random x values between 0 and 1000

# Generate y values with a linear correlation and a sine wave pattern
amplitude <- 400  # Amplitude of the sine wave
y <- .9 * x + rnorm(n, 0, 300) + amplitude * sin(0.01 * x)

cyclic_riser_df <-data.frame(time = x, expression = y) 
```

## egressR
```{r}
corrected_cyclic_riser_df <- egressR(
                      data_frame_to_build_model = cyclic_riser_df,
                      response_var = "expression",
                      predictor_variable = "time")
```

**view original and normalised data**
```{r}
#Original
ggplot(corrected_cyclic_riser_df, aes( x = time, y = expression))+
  geom_point()+
  theme_classic()+
  ggtitle("original cyclic data")

#Normalised data
ggplot(corrected_cyclic_riser_df, aes( x = time, y = normalisedexpressionfrom_time))+
  geom_point()+
  theme_classic()+
  ggtitle("detrended cyclic data")

```









