---
title: "README"
author: "LGD"
date: "20/05/2023"
output:
  github_document:
    toc: true
    toc_depth: 3
---

enGlimpse is a package of tools for **emgeezing** or **englimpsing** the output of plate based biology experiments. 
The two main functions are **emGeezen** and **enGlimpse** which both visualise experiment results in a plate format. The functions have different flavours, and **emGeezen** is recommended.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,results='hide', warning=FALSE}

#install devtools if needed
if(!require("devtools")) install.packages("devtools")
#load devtools
library(devtools)

#install lifeTimes from github
install_github("somaSystems/enGlimpse")

```




## Demonstration data
```{r}
#demonstration data in the format of a 96 well plate

set.seed(1)
df_to_glimpse <- data.frame(
  Row = rep(c(1:8), times = 12), #Rows as numbers
  Column = rep(c(1:12), each = 8), #Columns as numbers 
  exp_value = runif(96,-10,10)) #Measured variables

```

## emGeezen
- emGeeze (verb form of the noun "Geez"), which is Australian/NewZealand slang for "squiz","gander" or a quick look at something. The verb from comes from the "em" prefix, as in the phrase "a noble spirit embiggins the smallest person". 


```{r, warning=FALSE}

library(enGlimpse)
emGeezen(df_to_glimpse, variable_to_squiz ="exp_value" )

```

## enGlimpse
- enGlimpse (verb form of the noun "glimpse") is a package of tools for **englimpsing** the output of plate based biology experiments.  
- the main function is enGlimpse for visualising summary statistics of your plate based experiment

```{r}
enGlimpse(df_to_glimpse, picked_variable = "exp_value")
```

