---
title: "README"
author: "LGD"
date: "20/05/2023"
output:
  github_document:
    toc: true
    toc_depth: 3
---

enGlimpse is a package of tools for **emgeezing** or **englimpsing** the output of plate based biology experiments. 
The two main functions are **emGeezen** and **enGlimpse** which both visualise experiment results in a plate format. The functions have different flavours, and **emGeezen** is recommended.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation
```{r, echo = TRUE, results='hide', message = FALSE}

#install devtools if needed
if(!require("devtools")) install.packages("devtools")
#load devtools
library(devtools)

#install lifeTimes from github
install_github("somaSystems/enGlimpse")

```

## Demonstration data
```{r}
#demonstration data in the format of a 96 well plate

set.seed(1)
df_to_glimpse <- data.frame(
  Row = rep(c(1:8), times = 12), #Rows as numbers
  Column = rep(c(1:12), each = 8), #Columns as numbers 
  exp_value = runif(96,-10,10)) #Measured variables

```

## emGeezen
- emGeeze (verb form of the noun "Geez"), which is Australian/NewZealand slang for "squiz","gander" or a quick look at something. The verb from comes from the "em" prefix, as in the phrase "a noble spirit embiggins the smallest person". 


```{r, warning=FALSE}

library(enGlimpse)
glance(df_to_glimpse, variable_to_squiz ="exp_value" )

```

## enGlimpse
- enGlimpse (verb form of the noun "glimpse") is a package of tools for **englimpsing** the output of plate based biology experiments.  
- the main function is enGlimpse for visualising summary statistics of your plate based experiment

```{r}
squiz(df_to_glimpse, picked_variable = "exp_value")
```

## fastloadr

For loading an \*.RDS file instead of \*.csv. If you don't have an RDS *fastrloadr* makes one for next time. 

```{r}

# Create a data frame
df <- data.frame(phrase = c("I have an urge for swiftness", "I have a desire for rapidity", 
                            "I have a hunger for haste", "I have a yearning for velocity", 
                            "I have a craving for quickness"))

# Write the data frame to a CSV file
write.csv(df, file = "faster_please", row.names = FALSE)

# Now, let's use the function to read the CSV file. 
# If an RDS file with the same name doesn't exist in the same directory, 
# it will read the CSV file and save it as an RDS file.
fastdata <- fastloadr("faster_please.csv")

# Print the data
print(data)


```

The function reads in a path to a CSV file. If an RDS file with the same name and directory exists, it will read and return this RDS file. If such an RDS file does not exist, the function reads the CSV file, saves this data as an RDS file in the same directory, and then returns the data.
